---
title: "Final Report for Intro to Data Science"
output: html_notebook
---

-----------------------------------------------------------------------------------------------------------------------
## Instructor Notes
This is where the final project report write-up goes. 


Before you submit, make sure everything runs as expected.

You can add sections as you see fit. Make sure you have a section called "Introduction" at the beginning and a section called "Conclusion" at the end. The rest is up to you!

_Make use of your knowledge of Markdown to appropriately typeset this report!_
------------------------------------------------------------------------------------------------------------------------
# Final Report for Intro to Data Science: Steam Games


## Group Members

- Randy Kohila

- Isaiah Sarria

- Owen Telis

- John Levitt


## Introduction

Steam is a popular, online video game distributor with many other complementing features. Steams hosts community discussion threads, access to download community-made modifications to games sold on the platform, social media-like user profiles and friends lists that displays the users overall or recent video game activity, and sales events which are based on holidays or unique themes.

We want to analyze a dataset regarding Steam games to dive deep into the behavior of gamers on the platform.


## Packages

Loading any needed packages.

```{r}
library(tidyverse)

```




## The Dataset

The games.csv dataset has data collected for games on the popular game license selling platform, Steam, over the months from the years July 2012- Febuary 2021. The data set has records of 1258 games (also includes other miscellaneous pieces of software), and includes their titles, monthly player peaks, monthly average players at the same time, monthly gains/losses of players compared to the previous month, and the percentage of how closely the average players approach the peak.


```{r}
# Storing dataset in `games`
games <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-16/games.csv")
```


```{r}
# Finding the distinct number of `gamenames`
 dist_g <- games %>% 
  distinct(gamename)

dist_g
```


1. Can we prove that games generally lose popularity over time?

```{r}


g_apex <- games %>% 
  filter(gamename == "PAYDAY 2") %>% 
  filter(year %in% c(2018,2019,2020)) 


g_apex

ggplot(data = g_apex) +
  geom_line(aes(x = year, y = avg ))

 
```

```{r}


g_gta5 <- games %>% 
  filter(gamename == "Grand Theft Auto V") %>% 
  filter(year == 2020) 

g_gta5


ggplot(data = g_gta5) +
  geom_line(aes(x = month, y = avg, group = 1))

 
```




```{r}
g_rim <- games %>% 
  filter(gamename == "RimWorld") %>% 
  filter(year == 2020) 




plot_rim<- ggplot(data = g_rim) +
  geom_line(aes(x = month, y = avg, group = 1))

plot_rim

```

```{r}

g_m_underTale <- games %>% 
  filter(gamename == "Undertale") %>% 
  filter(month == "November") 

ggplot(data = g_m_underTale) +
  geom_line(aes(x = year, y = avg))



g_y_underTale <- games %>% 
  filter(gamename == "Undertale") %>% 
  filter(year == 2020) 

g_y_underTale

plot_undertale <- ggplot(data = g_y_underTale) +
  geom_line(aes( y = avg, x = month, group = 1))
  
  
  


```

```{r}
rim_and_under = ggplot() + 
  geom_line(data = g_rim, aes(x = month, y = avg, group = 1), color = "blue") +
  geom_line(data = g_y_underTale, aes(x = month, y = avg, group = 1), color = "red") +
  xlab("month") +
  ylab("avg players")

print(rim_and_under)
```




3. Which year do games have drastic drops or rises in popularity?
```{r}

g_top50 <- games %>% 
  filter(year == 2021) %>% 
  filter(month == "February") %>% 
  arrange(desc(avg)) %>% 
 head(50)


ggplot(data = g_top50) +
  geom_line(aes(x = gamename, y = avg, group = 1))

```



```{r}
games %>% 
  filter(gamename == "Counter-Strike: Global Offensive")
```

